

\newpage
\thispagestyle{plain}
\setcounter{page}{1}
\renewcommand{\thepage}{\roman{page}}

\begin{center}
    \Large\textbf{ABSTRACT}
\end{center}
\vspace{6pt}
Visually impaired individuals face significant challenges when navigating indoor environments, particularly in unfamiliar settings. Indoor spaces are often unpredictable, filled with obstacles, and designed with critical visual information intended for sighted individuals. These challenges create a reliance on external assistance, such as asking for help from strangers or using companions, which can diminish the independence of visually impaired individuals. 

This project aims to provide a solution through a wearable, easy-to-use system that guides and assists users by determining their position and detecting obstacles in their surroundings. 

The proposed system integrates four core components: Obstacle Detection, Localization, Customizable Guidance, and a Management Dashboard. These components work together to enhance the navigation experience for visually impaired individuals. The Obstacle Detection System uses ultrasonic sensors to identify obstacles in the user’s path and provides tactile feedback through vibration motors, enhancing spatial awareness. The Localization System uses QR codes as artificial landmarks to determine the user's position relative to the environment, providing accurate and reliable indoor localization. The Customizable Guidance System delivers tailored, location-specific instructions via the smartphone, helping users navigate effectively through designated areas. Additionally, the Management Dashboard allows building managers to easily integrate the system into their facilities by enabling them to generate, manage, and deploy QR codes within the building.

By integrating these components, the system ensures a practical and cost-effective solution for improving mobility, independence, and accessibility for visually impaired individuals, while also simplifying adoption for building managers.


\color{red}
- the result obtained

- the significance of the result or finding 
\color{black}

\vspace{18pt}
\noindent
\textbf{KEYWORDS:}  Localization; Obstacles Avoidance; Objects Detection, Customization; Guidance; Pose; Calibration; Assistive Technology; Smartphone Application; Accessibility Application
\vspace{3\baselineskip}