
\newpage
\addcontentsline{toc}{chapter}{References}
\renewcommand{\bibname}{References}

\begin{thebibliography}{9}
	\bibitem{Fiducial2021}
	Michail K., Brennan C., Sabrina C., Anand A., Camden W., \& Nikolaos
	V. (2021). Fiducial Markers for Pose Estimation. Journal of Intelligent \&
	Robotic Systems (2021) 101:71.
	https://link.springer.com/article/10.1007/s10846-020-01307-9
		
	\bibitem{Tiwari2016} Tiwari, V., "QR Code Technology and Its Applications," International Journal of Advanced Research in Computer Science and Software Engineering, vol. 6, no. 4, pp. 123-127, 2016.
	
	\bibitem{zhang2015}
	H. Zhang, C. Zhang, W. Yang and C. -Y. Chen, "Localization and navigation using QR code for mobile robot in indoor environment," 2015 IEEE International Conference on Robotics and Biomimetics (ROBIO), Zhuhai, China, 2015, pp. 2501-2506, doi: 10.1109/ROBIO.2015.7419715.
	
	\bibitem{ahmetovic2016}
	D. Ahmetovic, C. Gleason, C. Ruan, K. M. Kitani, H. Takagi and C. Asakawa, "NavCog: a navigational cognitive assistant for the blind," *Proceedings of the 18th International Conference on Human-Computer Interaction with Mobile Devices and Services*, Florence, Italy, 2016, pp. 90-99, doi: 10.1145/2935334.2935361.
	
	\bibitem{ibm2024}
	IBM, "What Is an API (Application Programming Interface)?," *IBM Topics*, 2024. [Online]. Available: https://www.ibm.com/topics/api. [Accessed: 28-Oct-2024].
	
	\bibitem{visual-paradigm}
	Visual Paradigm, "What Is Entity Relationship Diagram?," *Visual Paradigm*, 2024. [Online]. Available: https://www.visual-paradigm.com/guide/data-modeling/what-is-entity-relationship-diagram/. [Accessed: 28-Oct-2024].
	
	
	
	

	\bibitem{Lucag2017}
	Luca C., Gionata C., Francesco F., Alessandro F., Gianluca I., Andrea M. Federica V. (2017). A QR-code Localization System for Mobile Robots: Application to Smart Wheelchairs.
	https://ieeexplore.ieee.org/document/8098667
	
	\bibitem{kim2021}
	J.-I. Kim, H.-S. Gang, J.-Y. Pyun, and G.-R. Kwon, "Implementation of QR Code Recognition Technology Using Smartphone Camera for Indoor Positioning," Energies, vol. 14, no. 10, p. 2759, 2021, doi: 10.3390/EN14102759.
	
	\bibitem{lee2015}
	S. -J. Lee, G. Tewolde, J. Lim and J. Kwon, "QR-code based Localization for Indoor Mobile Robot with validation using a 3D optical tracking instrument," 2015 IEEE International Conference on Advanced Intelligent Mechatronics (AIM), Busan, Korea (South), 2015, pp. 965-970, doi: 10.1109/AIM.2015.7222664.
	
	\bibitem{kalaitzakis2021} 
	M. Kalaitzakis, B. Cain, S. Carroll, A. Ambrosi, C. Whitehead, and N. Vitzilaios, "Fiducial Markers for Pose Estimation: Overview, Applications, and Experimental Comparison of the ARTag, AprilTag, ArUco, and STag Markers," Journal of Intelligent \& Robotic Systems, vol. 101, no. 71, pp. 1-26, 2021, doi: 10.1007/s10846-020-01307-9.
	
	\bibitem{Aqeel Anwar}
	Aqeel Anwar, "What are Intrinsic and Extrinsic Camera Parameters in Computer Vision?", A detailed explanation of intrinsic and extrinsic camera parameters with the help of visualizations.
	https://towardsdatascience.com/what-are-intrinsic-and-extrinsic-camera-parameters-in-computer-vision-7071b72fb8ec
	
	\bibitem{kuribayashi2023}
	M. Kuribayashi, T. Ishihara, D. Sato, J. Vongkulbhisal, K. Ram, S. Kayukawa, H. Takagi, S. Morishima and C. Asakawa, "PathFinder: Designing a Map-less Navigation System for Blind People in Unfamiliar Buildings," *Proceedings of the 2023 CHI Conference on Human Factors in Computing Systems (CHI '23)*, New York, NY, USA, 2023, Article 41, pp. 1–16, doi: 10.1145/3544548.3580687.
	
	\bibitem{fraga2022}
	A. L. Fraga, X. Yu, W.-J. Yi, and J. Saniie, "Indoor Navigation System for Visually Impaired People using Computer Vision," *2022 IEEE International Conference on Electro Information Technology (eIT)*, Grand Forks, ND, USA, 2022, pp. 257-260, doi: 10.1109/eIT53694.2022.9800294.
	
	\bibitem{whichCameraLibToUse}
	https://developer.android.com/media/camera/choose-camera-library
	
	\bibitem{Tiwari2016}
	S. Tiwari, "An Introduction to QR Code Technology," 2016 International Conference on Information Technology (ICIT), Bhubaneswar, India, pp. 39-44, 2016, doi: 10.1109/ICIT.2016.021.
	
	\bibitem{leitch2023} S.G. Leitch, Q.Z. Ahmed, W.B. Abbas, M. Hafeez, P.I. Laziridis, P. Sureephong, and T. Alade, "On Indoor Localization Using WiFi, BLE, UWB, and IMU Technologies," Sensors, vol. 23, no. 20, pp. 8598, 2023, doi: 10.3390/s23208598.
	
	\bibitem{QRCodeMonkey2024} "QRCode Monkey - Free QR Code Generator," QRCode Monkey, Available: \url{https://www.qrcode-monkey.com}.
	
	\bibitem{QRTiger2024} "QR TIGER - Free QR Code Generator," QR Tiger, Available: \url{https://www.qrcode-tiger.com}.
	
	
	\bibitem{PyQRCode2024} "PyQRCode Documentation," PyQRCode, Available: \url{https://pyqrcode.readthedocs.io}.

	\bibitem{ZXing2024} "ZXing Decoder," ZXing Project, Available: \url{https://github.com/zxing/zxing}.

	\bibitem{CoreImage2024} "Core Image Framework," Apple Developer Documentation, Available: \url{https://developer.apple.com/documentation/coreimage}.

	\bibitem{Segno2024} "Segno - Python QR Code Generator," Segno Documentation, Available: \url{https://segno.readthedocs.io}.

	\bibitem{AVFoundation2024} "AVFoundation Framework," Apple Developer Documentation, Available: \url{https://developer.apple.com/documentation/avfoundation}.

	\bibitem{SebastianLague_AStar}
	https://www.youtube.com/watch?v=-L-WgKMFuhE\&list=
	PLFt AvWsXl0cq5Umv3pMC9SPnKjfp9eGW

	\bibitem{QRickit2024} "QRickit QR Code Decoder," QRickit, Available: \url{https://qrickit.com}.
\end{thebibliography}