\section{Test \& Evaluation}

To validate the effectiveness and usability of the proposed system, two evaluations will be conducted: an assessment of the overall user experience and a focused evaluation of the localization system.

\subsection{Evaluation of Overall Experience}

This evaluation focuses on the user's journey, excluding localization, as it is tested separately. A group of six participants will be blindfolded, with three using the system and three relying on traditional navigation methods. The evaluation will take place in an unfamiliar building. The participants’ experiences will be assessed using the following survey:

\subsubsection*{Survey Questions}
\begin{enumerate}
	\item How confident did you feel navigating the building?
	\item How easy was it to identify obstacles and avoid them?
	\item Did you find the instructions clear and helpful?
	\item How comfortable were you using the system during the task?
	\item Would you recommend this system to others with similar needs?
\end{enumerate}

Where the possible answers will be collected on a likert scale of Strongly Disagree, Disagree, Neutral, Agree, and Strong Agree. 


\subsection{Evaluation of Localization System}

To test the localization system's accuracy, the evaluation will take place in a controlled 4x4 meter room. Four QR codes will be placed on the walls encoding their global positions. The system will estimate its location based on the detected QR codes and compare the results to the actual known positions.

\subsubsection*{Evaluation Procedure}
\begin{enumerate}
	\item The user stands at predefined positions in the room, and the system records the estimated positions based on QR code data.
	\item The recorded positions are compared to the actual known coordinates.
	\item The error in localization is calculated as the Euclidean distance between the estimated and actual positions.
\end{enumerate}

This evaluation will determine the system’s precision and reliability in providing accurate localization data under ideal conditions. These results, combined with the user experience feedback, will provide a comprehensive assessment of the system's effectiveness.











