\section{Overview}

Navigating indoor environments poses significant challenges for individuals with visual impairments. These challenges stem not only from the absence of effective GPS signals indoors but also from the complexity of navigating unfamiliar spaces, which often lack accessible cues for orientation. Retail malls, hospitals, educational institutions, and other intricate spaces present obstacles that can impede mobility and independence for visually impaired individuals.

This project goes beyond solving the problem of indoor localization. It introduces a comprehensive navigation and guidance system that addresses multiple facets of the user experience. By leveraging QR codes as artificial landmarks, the system provides precise localization, enabling users to determine their position within an environment. Additionally, the system incorporates obstacle detection and real-time feedback through tactile and auditory alerts, enhancing spatial awareness and safety.

The proposed solution also offers a customizable guidance experience, allowing users to access location-specific instructions and tailored navigation paths. Furthermore, a user-friendly dashboard empowers building managers to integrate the system seamlessly into their facilities by managing and deploying QR codes efficiently. This end-to-end approach ensures that visually impaired individuals can navigate indoor spaces with confidence, independence, and ease.

By combining advanced localization, obstacle detection, and intuitive guidance, the system aims to deliver an accessible, and cost-effective solution that transforms the way visually impaired individuals navigate in unfamiliar building, as well as interacting with their surroundings.
