\section{Conclusion}

This project introduced Mosaned, a wearable and affordable indoor navigation system designed to enhance the independence of visually impaired individuals. By leveraging accessible technologies such as QR codes and smartphones, Mosaned effectively addresses the unique challenges of indoor navigation, providing real-time localization, context-aware guidance, and reliable obstacle detection. The integration of customizable IO components and support for accessibility features like TalkBack makes the system inclusive and user-friendly. Additionally, the management dashboard and database enable building administrators to efficiently deploy and maintain the system at scale. Experimental evaluation confirmed that Mosaned delivers accurate and dependable guidance, contributing significantly to user safety and autonomy in indoor spaces.

\section{Future Work}

While Mosaned fulfills its core objectives, several critical improvements are necessary for wider adoption and enhanced usability. The most urgent priority is transitioning the obstacle detection hardware to a fully wireless solution, as this will greatly improve comfort, wearability, and overall user experience. Establishing standardized guidelines for QR code placement, in collaboration with building managers and relevant stakeholders, is also essential to ensure consistent performance across diverse environments. Further, improving distance estimation and localization accuracy through advanced sensing or computer vision techniques will increase reliability, especially in more complex settings. Finally, conducting extensive real-world trials with a broader range of users and building types will be crucial for validating and refining the system, paving the way for future integration of additional assistive features such as AI-driven guidance and voice control.

\bigskip

In summary, Mosaned offers a promising foundation for accessible indoor navigation. The lessons learned and outlined future directions will help drive ongoing innovation, making indoor environments safer and more navigable for all.
